\section{Introduction}\label{sec:intro}

Most Internet communications begin with a client device sending DNS queries to
a recursive resolver, which in turn queries one or more name servers, which
ultimately refer the client to a server who can map the domain to an IP
address.
The \emph{response times} of these queries---the time 
to contact a recursive resolver, query various name servers, and return
the results---is important because the DNS underlies virtually all
communication on the Internet.

DNS did not originally take privacy and security into account: DNS queries
have historically been unencrypted, leaving users susceptible to
eavesdropping~\cite{schmitt2019:odns:pets}; queries can also be intercepted and
manipulated~\cite{jones2016detecting}.  To
address these types of privacy and security vulnerabilities, encrypted DNS
protocols have been developed and deployed, including DNS-over-HTTPS
(DoH)~\cite{rfc8484}. DoH enables clients to communicate with recursive resolvers
over HTTPS, providing privacy and security guarantees that DNS previously
lacked.

Most contemporary deployments of DoH have occurred in
browsers that provide limited options for
resolvers~\cite{ffChoices,chromeResolvers}.  Although DoH
protects against on-path eavesdropping, it does not prevent resolvers
\emph{themselves} from seeing the contents of DNS queries.  Thus, some have
argued that browser-based DoH deployments shift privacy concerns from
eavesdroppers to potential misuse by major DNS providers~\cite{vixie}.

\begin{table}[t]
\begin{footnotesize}
    \centering
    \addtolength{\tabcolsep}{-0.4em}
    \begin{tabular}{l|cccccc}
    \hline
    Browser & Cloudflare & Google & Quad9 & NextDNS & CleanBrowsing & OpenDNS
    \\
    \midrule
    Chrome    & \checkmark & \checkmark & & \checkmark & \checkmark & \checkmark \\
    Firefox  & \checkmark & & & \checkmark & & \\ 
    Edge   & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    Opera            & \checkmark & \checkmark & & & & \\
    Brave            & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    \bottomrule
    \end{tabular}
    \caption{Modern browsers provide only a few choices for encrypted DNS
    resolver, which we define as {\bf mainstream} resolvers.}
    \label{tab:SupportedResolvers}
\end{footnotesize}
\end{table}

Table~\ref{tab:SupportedResolvers} shows the DoH resolvers that have been deployed
to users of major browsers as of April 14,
2025~\cite{bravebrowser,edgebrowser,ffbrowser,chromebrowser,operabrowser}.  We
define the resolvers listed in Table~\ref{tab:SupportedResolvers} as {\em
mainstream}.
Yet, many other DoH resolvers have been deployed that are currently
not in use by major browser deployments~\cite{dnscrypt}---in other words,
there are many non-mainstream DoH resolver deployments.  

Previous studies have measured encrypted DNS performance, but they have mostly focused on mainstream DNS resolvers~\cite{hounsel2020comparing,hounsel2021can,hoang2020k,lu2019end-to-end}.
In this paper, we expand on these previous studies, exploring the performance
of all encrypted DNS resolvers---from a variety of global 
vantage points, as opposed to simply characterizing the mainstream DoH
providers from well-connected vantage points.
Towards this goal, we make the following contributions:
\begin{enumerate}
    \itemsep=-1pt
    \item We measure DoH response times a large list of resolvers, including
        both mainstream DoH resolvers that are included in major browser
        vendors {\em and} a large collection of non-mainstream resolvers.
%    \item We study whether users must use a major provider to experience acceptable DoH response times.
    \item We study how the performance of various DoH resolvers differ based
        on vantage point.
    \item We study the performance of DoH resolvers in home networks. 
\end{enumerate}
\noindent
To our knowledge, this paper presents the first study of DoH performance
measurements for non-mainstream resolvers, as well as the first comparison of
DoH performance across a variety of vantage points, for a large number of
resolvers.
To perform these experiments, we developed and released an open-source
tool for measuring encrypted DNS performance to replicate and extend these
results, and to support further research on DoH performance.

The rest of the paper is organized as follows.  Section~\ref{sec:background}
provides background on DNS, including the origin of encrypted DNS and related
standards, and discusses related work.  Section~\ref{sec:method} details our research questions, the
experiments we conducted to study these questions, and the limitations of the
study.  Section~\ref{sec:results} presents the results of these experiments.
Section~\ref{sec:discussion} discusses the implications
of these results and Section~\ref{sec:conclusion} gives possible directions for future work. 

